The Astropy Project: Building an open-science project and status of the v2.0 core package

### 2018-03-18 main.tex
Fixing minor bibtex issues
updated for v3.0 release

\subsubsection{Local Earth coordinate frames}
In addition to representing celestial
    coordinates, \astropypkg now supports specifying positions on the Earth in
    a number of different geocentric systems with the \texttt{EarthLocation}
    class.
    With this, \astropypkg now supports Earth-location-specific coordinate
    systems such as the altitude-azimuth (\texttt{AltAz}) or horizontal system.
    Transformations between \texttt{AltAz} and any Barycentric coordinate frame
    also requires specifying a time using the \astropyTime class from
    \texttt{astropy.time}.
    With this new functionality, many of the common tasks associated with
    observation planning can now be completed with \astropypkg or the
    \astropy-affiliated package \package{astroplan}\citep{astroplan_AAS}.

@@

Following the release of version 2.0, development on the next major version of
the \astropypkg core package (version 3.0) has already begun.
On top of planned changes and additions to the core package, we also plan to
overhaul the \astropy educational/learning materials and further
generalize the infrastructure utilities originally developed for the core
package for the benefit of the community.

@@

One of the most significant changes coming in this next major release will be
removing the support for \python 2 \citep{ape10}: future versions of \astropypkg
will only support \python 3.5 or higher.
Removing \python 2 support will allow the use of new \python 3-only features,
simplify the code base, and reduce the testing overhead for the package.
\astropypkg version 3.0 is currently scheduled for January 2018.

@@

The following individuals would like to recognize support for their personal contributions.
HMG was supported by the National Aeronautics and Space Administration through the
Smithsonian Astrophysical Observatory contract SV3-73016 to MIT for Support of the Chandra X-Ray Center, which is
operated by the Smithsonian Astrophysical Observatory for and on behalf of the National Aeronautics Space
Administration under contract NAS8-03060. JTV was supported by the UW eScience Institute, via grants from the Moore
Foundation, the Sloan Foundation, and the Washington Research Foundation. SMC acknowledges the National Research
Foundation of South Africa. TLA was supported by NASA contract NAS8-03060. Support for EJT. was provided by NASA
through Hubble Fellowship grant No. 51316.01 awarded by the Space Telescope Science Institute, which is operated by
the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS 5-26555, as well as a
Giacconi Fellowship. MB was supported by the FONDECYT regular project 1170618 and the MINEDUC-UA projects codes
ANT 1655 and ANT 1656. DH was supported through the SFB 881 ``The Milky Way System'' by the German Research Foundation
(DFG). WEK was supported by an ESO Fellowship. C.M. is supported by NSF grant AST-1313484. SP was supported by
grant AYA2016-75808-R (FEDER) issued by the Spanish government. JEHT was supported by the Gemini Observatory, which
is operated by the Association of Universities for Research in Astronomy, Inc., on behalf of the international
Gemini partnership of Argentina, Brazil, Canada, Chile, and the United States of America.  YPB was supported by 
the Korea Astronomy and Space Science Institute under the R\&D program supervised by the Ministry of Science, 
ICT and Future Planning.

>>>>

\subsubsection{Local Earth coordinate frames}
In addition to representing celestial
    coordinates, \astropypkg now supports specifying positions on the Earth in
    a number of different geocentric systems with the \texttt{EarthLocation}
    class.
    With this, \astropypkg now supports Earth-location-specific coordinate
    systems such as the altitude-azimuth (\texttt{AltAz}) or horizontal system.
    Transformations between \texttt{AltAz} and any Barycentric coordinate frame
    also requires specifying a time using the \astropyTime class from
    \texttt{astropy.time}.
    With this new functionality, many of the common tasks associated with
    observation planning can now be completed with \astropypkg or the
    \astropy-affiliated package \package{astroplan}\citep{astroplan}.

@@

Following the release of version 2.0, development on the next major version of
the \astropypkg core package (version 3.0) began.
On top of planned changes and additions to the core package, we also plan to
overhaul the \astropy educational/learning materials and further
generalize the infrastructure utilities originally developed for the core
package for the benefit of the community.

@@

One of the most significant changes coming in this next major release will be
removing the support for \python 2 \citep{ape10}: future versions of \astropypkg
will only support \python 3.5 or higher.
Removing \python 2 support will allow the use of new \python 3-only features,
simplify the code base, and reduce the testing overhead for the package.
\astropypkg version 3.0 ws released in February 2018.

@@

The following individuals would like to recognize support for their personal contributions.
HMG was supported by the National Aeronautics and Space Administration through the
Smithsonian Astrophysical Observatory contract SV3-73016 to MIT for Support of the Chandra X-Ray Center, which is
operated by the Smithsonian Astrophysical Observatory for and on behalf of the National Aeronautics Space
Administration under contract NAS8-03060. JTV was supported by the UW eScience Institute, via grants from the Moore
Foundation, the Sloan Foundation, and the Washington Research Foundation. SMC acknowledges the National Research
Foundation of South Africa. MVB was supported by NASA's Planetary Astronomy Program.
TLA was supported by NASA contract NAS8-03060. Support for EJT. was provided by NASA
through Hubble Fellowship grant No. 51316.01 awarded by the Space Telescope Science Institute, which is operated by
the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS 5-26555, as well as a
Giacconi Fellowship. MB was supported by the FONDECYT regular project 1170618 and the MINEDUC-UA projects codes
ANT 1655 and ANT 1656. DH was supported through the SFB 881 ``The Milky Way System'' by the German Research Foundation
(DFG). WEK was supported by an ESO Fellowship. C.M. is supported by NSF grant AST-1313484. SP was supported by
grant AYA2016-75808-R (FEDER) issued by the Spanish government. JEHT was supported by the Gemini Observatory, which
is operated by the Association of Universities for Research in Astronomy, Inc., on behalf of the international
Gemini partnership of Argentina, Brazil, Canada, Chile, and the United States of America.  YPB was supported by
the Korea Astronomy and Space Science Institute under the R\&D program supervised by the Ministry of Science,
ICT and Future Planning.
